Active Learning for SAT Solver Benchmarking {\large (extended and revised version)}

### 2024-05-27 paper_jar/paper.tex
Fix plot path

\begin{figure}[tb]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[height=4.123cm]{../plots/cm2labels.pdf}
		\caption{Timeout prediction.}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[height=4.228cm]{../plots/cm3labels.pdf}
		\caption{$C_3$ cluster prediction.}
	\end{subfigure}
	\caption{Confusion matrices for predicting timeouts and $C_3$ cluster labels.}
	\label{fig:confusion-matrices}
\end{figure}

@@

% Amount of significant solver pairs (Wilcoxon signed-rank, 5% alpha):
% PAR-2:   684/756 = 0.9048
% timeout: 660/756 = 0.8730
% k=3:     662/756 = 0.8757
% k=4:     662/756 = 0.8757
% k=5:     662/756 = 0.8757
\begin{figure}[tb]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{../plots/par2sigdiff.pdf}
		\caption{PAR-2 scores.}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{../plots/timeoutsigdiff.pdf}
		\caption{Timeouts.}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{../plots/s3sigdiff.pdf}
		\caption{$s_3$ scores.}
	\end{subfigure}
	\caption{Solver pairs with significant differences regarding their scorings are colored white, non-significant ones black. Solvers are ordered identically to Table~\ref{tab:ranking}.}
	\label{fig:solver-confusion-matrices}
\end{figure}

@@

\begin{figure}[tbp!]
  \centering
  \begin{subfigure}{1.0\textwidth}
    \resizebox{\textwidth}{!}{
      \graphicspath{{../plots/}}
      \input{../plots/anni_train_color_ranking.pgf}
    }
    \caption{Ranking approaches.}
    \label{fig:annitraincolorranking}
  \end{subfigure}
  \\
  \vspace{0.2cm}
  \begin{subfigure}{1.0\textwidth}
    \resizebox{\textwidth}{!}{
      \graphicspath{{../plots/}}
      \input{../plots/anni_train_color_selection.pgf}
    }
    \caption{Selection approaches.}
    \label{fig:annitraincolorselection}
  \end{subfigure}
  \\
  \vspace{0.2cm}
  \begin{subfigure}{1.0\textwidth}
    \resizebox{\textwidth}{!}{
      \graphicspath{{../plots/}}
      \input{../plots/anni_train_color_stopping.pgf}
    }
    \caption{Stopping criteria.}
    \label{fig:annitraincolorstopping}
  \end{subfigure}
  \caption{
    $O_{\operatorname{rt}}$-$O_{\operatorname{acc}}$-diagrams (cf. Section~\ref{sec:exdesign:eval}) comparing different hyperparameter instantiations of our active-learning framework on the hyperparameter-tuning dataset.
    The x-axis shows the ratio of total solver runtime on the sampled instances relative to all instances.
    The y-axis shows the ranking accuracy.
    Each line represents the front of Pareto-optimal configurations for the respective hyperparameter instantiation.
  }
  \label{fig:e2eallsolvers}
\end{figure}

@@

\begin{figure}[tb!]
  \centering
  \begin{subfigure}{0.4775\textwidth}
    \resizebox{\textwidth}{!}{
      \graphicspath{{../plots/}}
      \input{../plots/anni_train_optimization_goal.pgf}
    }
    \caption{Runtime vs. Instances}
    \label{fig:annitrainoptgoalruntime}
  \end{subfigure}
  \begin{subfigure}{0.5125\textwidth}
    \resizebox{\textwidth}{!}{
      \graphicspath{{../plots/}}
      \input{../plots/anni_train_delta_acc.pgf}
    }
    \caption{Runtime vs. Accuracy}
    \label{fig:annitrainoptgoalacc}
  \end{subfigure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=0.6\textwidth]{../plots/instoccs.pdf}
  \caption{Frequency with which individual problem instances are selected within all active-learning benchmarks. Instances that are chosen more frequently are intuitively more important for distinguishing solver runtimes. Results are on the full dataset with cross-validation over all solvers.}
  \label{fig:instoccs}
\end{figure}

\begin{figure}[tb]
  \centering
  \resizebox{0.85\textwidth}{!}{
    \graphicspath{{../plots/}}
    \input{../plots/anni_final_families.pgf}
  }
  \caption{
    Scatter plot illustrating the relative importance of different instance families for ranking on the full dataset. The x-axis depicts the frequency of instance families in the dataset, while the y-axis represents the average frequency in the samples selected by active learning. The dashed line represents families that occur with the same frequency in the dataset and samples. Results are on the full dataset with cross-validation over all solvers.
  }
  \label{fig:annifinalfamilies}
\end{figure}

>>>>

\begin{figure}[tb]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[height=4.123cm]{plots/cm2labels.pdf}
		\caption{Timeout prediction.}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[height=4.228cm]{plots/cm3labels.pdf}
		\caption{$C_3$ cluster prediction.}
	\end{subfigure}
	\caption{Confusion matrices for predicting timeouts and $C_3$ cluster labels.}
	\label{fig:confusion-matrices}
\end{figure}

@@

% Amount of significant solver pairs (Wilcoxon signed-rank, 5% alpha):
% PAR-2:   684/756 = 0.9048
% timeout: 660/756 = 0.8730
% k=3:     662/756 = 0.8757
% k=4:     662/756 = 0.8757
% k=5:     662/756 = 0.8757
\begin{figure}[tb]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{plots/par2sigdiff.pdf}
		\caption{PAR-2 scores.}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{plots/timeoutsigdiff.pdf}
		\caption{Timeouts.}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{plots/s3sigdiff.pdf}
		\caption{$s_3$ scores.}
	\end{subfigure}
	\caption{Solver pairs with significant differences regarding their scorings are colored white, non-significant ones black. Solvers are ordered identically to Table~\ref{tab:ranking}.}
	\label{fig:solver-confusion-matrices}
\end{figure}

@@

\begin{figure}[tbp!]
  \centering
  \begin{subfigure}{1.0\textwidth}
    \resizebox{\textwidth}{!}{
      \graphicspath{{plots/}}
      \input{plots/anni_train_color_ranking.pgf}
    }
    \caption{Ranking approaches.}
    \label{fig:annitraincolorranking}
  \end{subfigure}
  \\
  \vspace{0.2cm}
  \begin{subfigure}{1.0\textwidth}
    \resizebox{\textwidth}{!}{
      \graphicspath{{plots/}}
      \input{plots/anni_train_color_selection.pgf}
    }
    \caption{Selection approaches.}
    \label{fig:annitraincolorselection}
  \end{subfigure}
  \\
  \vspace{0.2cm}
  \begin{subfigure}{1.0\textwidth}
    \resizebox{\textwidth}{!}{
      \graphicspath{{plots/}}
      \input{plots/anni_train_color_stopping.pgf}
    }
    \caption{Stopping criteria.}
    \label{fig:annitraincolorstopping}
  \end{subfigure}
  \caption{
    $O_{\operatorname{rt}}$-$O_{\operatorname{acc}}$-diagrams (cf. Section~\ref{sec:exdesign:eval}) comparing different hyperparameter instantiations of our active-learning framework on the hyperparameter-tuning dataset.
    The x-axis shows the ratio of total solver runtime on the sampled instances relative to all instances.
    The y-axis shows the ranking accuracy.
    Each line represents the front of Pareto-optimal configurations for the respective hyperparameter instantiation.
  }
  \label{fig:e2eallsolvers}
\end{figure}

@@

\begin{figure}[tb!]
  \centering
  \begin{subfigure}{0.4775\textwidth}
    \resizebox{\textwidth}{!}{
      \graphicspath{{plots/}}
      \input{plots/anni_train_optimization_goal.pgf}
    }
    \caption{Runtime vs. Instances}
    \label{fig:annitrainoptgoalruntime}
  \end{subfigure}
  \begin{subfigure}{0.5125\textwidth}
    \resizebox{\textwidth}{!}{
      \graphicspath{{plots/}}
      \input{plots/anni_train_delta_acc.pgf}
    }
    \caption{Runtime vs. Accuracy}
    \label{fig:annitrainoptgoalacc}
  \end{subfigure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=0.6\textwidth]{plots/instoccs.pdf}
  \caption{Frequency with which individual problem instances are selected within all active-learning benchmarks. Instances that are chosen more frequently are intuitively more important for distinguishing solver runtimes. Results are on the full dataset with cross-validation over all solvers.}
  \label{fig:instoccs}
\end{figure}

\begin{figure}[tb]
  \centering
  \resizebox{0.85\textwidth}{!}{
    \graphicspath{{plots/}}
    \input{plots/anni_final_families.pgf}
  }
  \caption{
    Scatter plot illustrating the relative importance of different instance families for ranking on the full dataset. The x-axis depicts the frequency of instance families in the dataset, while the y-axis represents the average frequency in the samples selected by active learning. The dashed line represents families that occur with the same frequency in the dataset and samples. Results are on the full dataset with cross-validation over all solvers.
  }
  \label{fig:annifinalfamilies}
\end{figure}
